QPLIB: A Library of Quadratic Programming Instances

### 2017-01-29 QPLIB-3.tex
make clear that variable bounds were not counted for binary variables, more about neg->hard ev.

For each instance of the starting set, we collected important characteristics
which allowed us to classify the instances into the QP categories described in
\S~\ref{sec:QPbasic}. As far as the variable types are concerned, we
collected the following information:
%
\begin{itemize}
 \item number of binary variables; % (\emph{\# bin}),
 %
 \item number of integer variables; % (\emph{\# int}),
 %
 \item number of continuous variables. % (\emph{\# cont}).
\end{itemize}
%
If at least one binary or integer variable is present, then the instance is
categorized as \emph{discrete}, otherwise it is categorized as \emph{continuous}.
As far as the objective function is concerned, we gathered the following
information:
%
\begin{itemize}
 \item percentage of negative eigenvalues of the $Q^0$ matrix;
       % (\emph{\% neg eig}),
 %
 \item density of the $Q^0$ matrix (number of nonzero entries divided by the total
       number of entries). %(\emph{\% dens}).
\end{itemize}
%

The number of negative (i.e., smaller than $-10^{-16}$) eigenvalues of $Q^0$ allows us to identify the
objective function type, as in presence of at least one negative eigenvalue
the objective function is non convex. Finally, as far as the constraint types
are concerned, we collected the following information:
%
\begin{itemize}
 \item number of linear constraints, % (\emph{\# lin}),
 %
 \item number of quadratic constraints, % (\emph{\# quad}),
 %
 \item number of convex constraints, % (\emph{\# conv}),
 %
 \item number of box constraints. %(\emph{\# box}).
\end{itemize}
%
A constraint is considered quadratic if it contains at least one nonzero in
the quadratic term. Among the quadratic constraints, the ones with only
non-negative eigenvalues are classified as convex constraints.
Note that this might lead to classify some instances that have conic constraints as non-convex ones, although their feasible region is in fact convex. However, only some solvers are capable of properly exploiting this property.
 All this information allowed us to analyse the gathered instances and to perform the
filters described in the the next paragraph.

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  2 \\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   14\\[1.2 ex]
\multirow{2}*{Concave (if max)}
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
                    & Linear    &   2\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]  % there are actually QBB due to the {0,1} bounds on the binary variables
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   9\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & Integer & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}

>>>>

For each instance of the starting set, we collected important characteristics
which allowed us to classify the instances into the QP categories described in
\S~\ref{sec:QPbasic}. As far as the variable types are concerned, we
collected the following information:
%
\begin{itemize}
 \item number of binary variables; % (\emph{\# bin}),
 %
 \item number of integer variables; % (\emph{\# int}),
 %
 \item number of continuous variables. % (\emph{\# cont}).
\end{itemize}
%
If at least one binary or integer variable is present, then the instance is
categorized as \emph{discrete}, otherwise it is categorized as \emph{continuous}.
As far as the objective function is concerned, we gathered the following
information:
%
\begin{itemize}
 \item percentage of positive and negative eigenvalues of the $Q^0$ matrix;
       % (\emph{\% neg eig}),
 %
 \item density of the $Q^0$ matrix (number of nonzero entries divided by the total
       number of entries). %(\emph{\% dens}).
\end{itemize}
%

The number of positive (i.e., larger than $10^{-16}$) and negative (i.e., smaller than $-10^{-16}$) eigenvalues of $Q^0$ allows us to identify the
objective function type, as in presence of at least one negative (positive) eigenvalue
the objective function is non convex (non concave). Finally, as far as the constraint types
are concerned, we collected the following information:
%
\begin{itemize}
 \item number of linear constraints, % (\emph{\# lin}),
 %
 \item number of quadratic constraints, % (\emph{\# quad}),
 %
 \item number of convex constraints, % (\emph{\# conv}),
 %
 \item number of variable bounds (for non-binary variables). %(\emph{\# box}).
\end{itemize}
%
A constraint is considered quadratic if it contains at least one nonzero in
the quadratic term. Among the quadratic constraints, the ones with only
non-negative eigenvalues are classified as convex constraints.
Note that this might lead to classify some instances that have conic constraints as non-convex ones, although their feasible region is in fact convex. However, only some solvers are capable of properly exploiting this property.
 All this information allowed us to analyse the gathered instances and to perform the
filters described in the the next paragraph.

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  2 \\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   14\\[1.2 ex]
\multirow{2}*{Concave (if max)}
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
                    & Linear    &   2\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex] on the binary variables
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   9\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & Integer & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}
